---
title: "EDA after cleaning"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

## Assumptions made during cleaning

In the diagnosis column "Cerebrovascular disease" covers everything and is essentially the "All" category. There were originally 3 sub-categories but these didn't add up to the total value under "Cerebrovascular disease". This is because there are some other diagnosis (with ICD codes I62, I65, I66-69) which fall outwith these sub-categories. For this reason a 4th sub-category was created called "Other CVD". 

There were a lot of missing values for Orkney, Shetland and Western Isles due to confidentiality. These were converted to zeros. 

```{r}
activity_hb <- read_csv(here("clean_data/activity_hb.csv")) 

mortality_hb <- read_csv(here("clean_data/mortality_hb.csv")) 

activity_ca <- read_csv(here("clean_data/activity_ca.csv")) 
```

```{r}
activity_hb %>% 
  select(where(is.character)) %>% 
  map(unique)
```



```{r}
activity_hb %>% 
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```

```{r, checking 'other cvd' cleaning code worked}
mortality_hb %>% 
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All" &
           diagnosis != "Cerebrovascular Disease") %>% 
  group_by(year) %>% 
  summarise(total = sum(number_of_deaths))
  
mortality_hb %>% 
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All" &
           diagnosis == "Cerebrovascular Disease") %>% 
  group_by(year) %>% 
  summarise(total = sum(number_of_deaths))
```

## Q2 Demographics effect on diagnosis (just activity data)
### Age - Discharge Data

Look at CVD by age first

```{r}
activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = age), position = "dodge")

activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, crude_rate)) +
  geom_col(aes(fill = age), position = "dodge")

activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, easr)) +
  geom_col(aes(fill = age), position = "dodge")
```

The crude rate and easr data shows a different pattern than the raw values. The number of discharges for 45-64 year olds and 65-74 years olds is similar but when this is adjusted for 100,000 of population (ie the crude rate) the number of discharges for 65-74 years olds is much higher. This is likely caused by the fact that the younger age range covers 20 years whereas the older one covers 10 years and also there will be fewer people in the older age range because people will have died. 

### Age - incidence data

```{r}
incidence <- read_csv(here("clean_data/incidence.csv"))
```


```{r}
incidence %>% 
  filter(hbr_name == "Scotland",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, incidence)) +
  geom_col(aes(fill = age), position = "dodge")
```


The incidence data looks very similar to discharge data. 


### Age - Discharge Data - Diagnosis

```{r}
activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y")

activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, crude_rate)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y")

activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, easr)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y")
```

Even after age adjustment subarachnoid haemorrhage has a different pattern to the other diagnoses. The other conditions show a distinct age related trend, with more discharges as age increases. Subarachnoid haemorrhage shows similar levels of discharge across all three age groups over 45. 

No need to show the data by year, let's show a 10 year average

```{r, warning = FALSE, message = FALSE}
activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", "TIAs and related syndromes",
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(age, diagnosis) %>% 
  summarise(total_discharges = mean(number_of_discharges)) %>% 
  ggplot(aes(age, total_discharges)) +
  geom_col(aes(fill = diagnosis)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#f084b6", "#9e8fcb", "#6d95bf"))



activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
                                                  "TIAs and related syndromes",
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(age, diagnosis) %>% 
  summarise(mean_crude_rate = mean(crude_rate)) %>% 
  ggplot(aes(age, mean_crude_rate)) +
  geom_col(aes(fill = diagnosis)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#f084b6", "#9e8fcb", "#6d95bf"))



activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
                                                  "TIAs and related syndromes",
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(age, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(age, mean_easr)) +
  geom_col(aes(fill = diagnosis)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#f084b6", "#9e8fcb", "#6d95bf"))
```



Same data below but displayed differently. The plots faceted on diagnosis (as above) are more informative

```{r}
activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge") +
  facet_wrap(~age, scales = "free_y")
```

### Age - Incidence Data - Diagnosis

```{r}
incidence %>% 
  filter(hbr_name == "Scotland",
         sex == "All",
         !age %in% c("All", "under 75")) %>% 
  ggplot(aes(year, incidence)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y")
```

Because there are only 

### Sex - Discharge Data

```{r}
activity_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = sex), position = "dodge")

activity_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, crude_rate)) +
  geom_col(aes(fill = sex), position = "dodge")

activity_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, easr)) +
  geom_col(aes(fill = sex), position = "dodge")
```



```{r, warning = FALSE, message = FALSE}
activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", "TIAs and related syndromes",
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(sex, diagnosis) %>% 
  summarise(mean_discharges = mean(number_of_discharges)) %>% 
  ggplot(aes(sex, mean_discharges)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_fc() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey30"))



activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
                                                  "TIAs and related syndromes",
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
          age == "All", 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(sex, diagnosis) %>% 
  summarise(mean_crude_rate = mean(crude_rate)) %>% 
  ggplot(aes(sex, mean_crude_rate)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_fc() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey30"))



activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
                                                  "TIAs and related syndromes",
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(sex, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(sex, mean_easr)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_fc() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey30"))

```




## Investigation into combining datasets

Mortality is the simpler and shorter dataset but it is already by year which is what we want, so lets try butchering the activity dataset. 

```{r}
activity_hb_by_cal_year <- activity_hb %>% 
  mutate(number_of_discharges_75pc = 0.75 * number_of_discharges,
         number_of_discharges_25pc = 0.25 * number_of_discharges, .before = hbr) %>% 
  arrange(hbr, admission_type, age, sex, diagnosis) %>% 
  mutate(year = str_extract(financial_year, "^[0-9]{4}"), .after = financial_year) %>% 
  mutate(year_num_discharges = number_of_discharges_75pc + lag(number_of_discharges_25pc),
         .before = hbr) %>% 
  select(-c(number_of_discharges_75pc, number_of_discharges_25pc)) %>% 
# remove all 2009 rows as these will be created by adding 2021 data. 
  filter(year != 2009)
  
```

The plots below compare the newly created calendar year data and original data and there isn't much difference. 

```{r}
activity_hb_by_cal_year %>% 
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")


activity_hb_by_cal_year %>% 
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(year, year_num_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")

```
Checking further plots - by age

```{r}
activity_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = age), position = "dodge")

activity_hb_by_cal_year %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, year_num_discharges)) +
  geom_col(aes(fill = age), position = "dodge")
```

Again this looks good so I think the code has done what I want. Now how to add in mortality data?

```{r}
# Filter activity data on admission type = all as mortality data doesn't have 
# admission type. 

combined_by_cal_year <- activity_hb_by_cal_year %>% 
  filter(admission_type == "All") %>% 
  mutate(year = as.numeric(year)) %>% 
  left_join(mortality_hb, by = c("year", "hbr", "age", "sex", "diagnosis"))



```

Ok so this works but not sure whether it is valid - also still need to convert crude rate and easr.  


## Q3 Number of cases by health board vs by local authority

Is isn't clear what number of cases refers to in this questions. The wording is different from the other questions. The incidences by health board and council area are available from the excel pivot tables. Lets have a look at the data we have first and see how we can view it. 

Combining Orkney, Shetland and Western Isles into one group called Islands

```{r}
islands <- activity_hb %>% 
  filter(hbr_name %in% c("Orkney", "Shetland", "Western Isles")) %>% 
  group_by(financial_year, admission_type, age, sex, diagnosis) %>% 
  summarise(number_of_discharges = sum(number_of_discharges),
            crude_rate = mean(crude_rate),
            easr = mean(easr)) %>% 
  mutate(hbr_name = "Islands")

activity_hb_islands <- activity_hb %>% 
  filter(!hbr_name %in% c("Orkney", "Shetland", "Western Isles")) %>% 
  bind_rows(islands)

activity_hb_islands %>% 
  select(where(is.character)) %>% 
  map(unique)

```



```{r}
activity_hb %>% 
  filter(!financial_year %in% c("2009/10", "2010/11", "2011/12")) %>% 
  filter(hbr == "S92000003" &
          age == "All" &
          sex == "All" &
          admission_type == "All" &
          diagnosis != "Cerebrovascular Disease") %>% 
  group_by(diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  mutate(diagnosis = fct_reorder(diagnosis, mean_easr)) %>% 
  ggplot(aes(diagnosis, mean_easr)) +
  geom_col(fill = c("#6d95bf", "#999999", "#9e8fcb", "#f084b6")) +
  theme_fc() +
  labs(title = "Discharges by Cerebrovascular Disease Diagnosis",
       subtitle = "10 year average", 
       y = "EASR",
       x = "CVD Diagnosis") +
  coord_flip() +
  # code to wrap text so it goes over two lines
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) 



activity_hb_islands %>% 
  mutate(hbr_name = recode(hbr_name, "Greater Glasgow & Clyde" = "Grtr Glasgow & Clyde")) %>% 
  filter(!financial_year %in% c("2009/10", "2010/11", "2011/12")) %>% 
  filter(hbr_name != "Scotland",
         sex == "All",
         admission_type == "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>% 
  group_by(hbr_name, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  mutate(diagnosis = fct_reorder(diagnosis, mean_easr)) %>% 
  ggplot(aes(diagnosis, mean_easr)) +
  geom_col(aes(fill = diagnosis)) +
  facet_wrap(~hbr_name) +
  coord_flip() +
  theme_fc() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 20)) +
  scale_fill_manual(values = c("#9e8fcb", "#6d95bf", "#f084b6", "#999999")) +
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 10, colour = "grey30"),
        axis.text.y = element_text(size = 8)
        )
```

What is this graph telling us and what do we want to know. 

```{r}
activity_hb_islands %>% 
  mutate(hbr_name = recode(hbr_name, "Greater Glasgow & Clyde" = "Grtr Glasgow & Clyde")) %>% 
  filter(!financial_year %in% c("2009/10", "2010/11", "2011/12")) %>% 
  filter(hbr_name != "Scotland",
         sex == "All",
         admission_type == "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>% 
  group_by(hbr_name, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  mutate(diagnosis = fct_reorder(diagnosis, mean_easr)) %>% 
#  group_by(hbr_name) %>% 
#  mutate(total_easr = sum(mean_easr)) %>% 
#  mutate(percent_easr = mean_easr / total_easr * 100) %>% 
  ggplot(aes(diagnosis, mean_easr)) +
  geom_col(aes(fill = hbr_name), position = "dodge")
```

I don't think either of the above graph are showing much of interest

```{r}
activity_hb_islands %>% 
    mutate(start_fin_year = as.numeric(str_extract(financial_year, "^[0-9]{4}")), 
         .after = financial_year) %>% 
  select(-financial_year, -hbr) %>%
  filter(hbr_name != "Scotland",
         sex == "All",
         admission_type == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(start_fin_year, easr)) +
  geom_point(aes(colour = hbr_name)) +
  geom_smooth(method = lm, colour = "black", linewidth = 0.4, se = FALSE) +
  facet_wrap(~hbr_name) +  
#  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., 
#                                        sep = "~~~~"))) +
# plots were coloured according to whether they changed by over or under 100 over the 13 year period
      scale_colour_manual(values = c("green", "orange", "red", "orange","green", "red", "green", "orange","orange", "green", "red", "orange")) +
#  theme_fc() +
    theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 10, colour = "grey30"),
        axis.text.y = element_text(size = 8))
```

```{r}
health_boards
```







```{r}
activity_ca %>% 
  filter(ca != "S92000003",
         sex == "All",
         admission_type == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(financial_year, easr)) +
  geom_point() +
  facet_wrap(~ca_name)
```








## Q4 Any differences in mortality rates for different types of strokes? Does this vary with demographcis. 

I think the questions are a bit mixed up and it might be better to present them in a different way. In question 2 it talks about stroke diagnoses when I think it means discharges. 


```{r}
mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```



### Age - Mortality Data

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = age), position = "dodge")

mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, crude_rate)) +
  geom_col(aes(fill = age), position = "dodge")

mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, easr)) +
  geom_col(aes(fill = age), position = "dodge")
```

Mortality follows a distinct age related trend, with number of deaths increasing with age. 

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2)

mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(year, crude_rate)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2)

mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(year, easr)) +
  geom_col(aes(fill = age), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2)
```




### Sex - Mortality Data

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         age == "All", 
         diagnosis == "Stroke") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = sex), position = "dodge")

mortality_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         age == "All", 
         diagnosis == "Stroke") %>% 
  ggplot(aes(year, crude_rate)) +
  geom_col(aes(fill = sex), position = "dodge")

mortality_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         age == "All", 
         diagnosis == "Stroke") %>% 
  ggplot(aes(year, easr)) +
  geom_col(aes(fill = sex), position = "dodge")
```

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003",
         sex != "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = sex), position = "dodge") +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2)
```

Investigating spike in males deaths from sub haem in 2020


```{r}
mortality_hb %>% 
  filter(hbr != "S92000003",
         sex == "Male",
         !age %in% c("All", "under 75"), 
         diagnosis == "Subarachnoid Haemorrhage") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = sex), position = "dodge") +
  facet_wrap(~hbr_name)
```

We see the spike in Glasgow, Dumfries, Forth Valley and Lothian. 