---
title: "EDA before cleaning"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

```{r, message = FALSE}
library(tidyverse)
library(here)
library(janitor)
library(purrr)
```

```{r, message = FALSE}
mortality_hb <- read_csv(here("raw_data/stroke_mortalitybyhbr.csv")) %>% 
  clean_names()

activity_hb <- read_csv(here("raw_data/stroke_activitybyhbr.csv")) %>% 
  clean_names()
```

```{r}
skimr::skim(activity_hb)
```

## Missing Data

Data is missing for confidentiality reasons (it has statistical term "c") because the numbers are so low they would allow identification of individuals. Original plan was to change values to 1 but this is complicated by the fact a lot of the values are derived so, for example, we'd need to change Male and Female to one and then All to 2 and then add this to overall total and Scotland total. 
All missing data is from orkney, shetland and western isles. 
3739 missing rows. 
There is no age group data for these 3 health boards but there is data under age_group = All. 

Let change all NAs to zero, the numbers are clearly low and we can't justifying guessing an actualy number. 


```{r}
activity_hb %>% 
  filter(is.na(number_of_discharges)) %>%  # 3739
  filter(is.na(admission_type_qf)) %>% # 2443
  filter(is.na(age_group_qf)) %>%  # 1782
  filter(is.na(sex_qf)) # 1092
```

1092 rows of data will be affected (and these will feed into all the other totals) which isn't ideal but it is over 3 health boards and 13 years. When looking at the data in the graph below it seems there is total data but not data broken down into age groups, 


```{r}
activity_hb %>% 
  filter(hbr == "S08000028") %>% 
#  filter(age_group != "All") %>% 
  group_by(financial_year, sex) %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = sex), position = "dodge")
```





```{r}
mortality_hb %>% 
  select(where(is.character)) %>% 
  map(unique)
```

```{r}
activity_hb %>% 
  select(where(is.character)) %>% 
  map(unique)
```


```{r}
activity_hb %>% 
  filter(hbr == "S92000003" &
           age_group == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003" &
           age_group == "All" &
           sex == "All") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```

```{r}
mortality_hb %>% 
  filter(!hbr == "S92000003" &
           age_group == "All" &
           sex == "All") %>% 
  ggplot(aes(year, number_of_deaths)) +
  geom_col(aes(fill = diagnosis), position = "dodge") +
  facet_wrap(~hbr)
```

```{r}
mortality_hb_2022 <- read_csv(here("raw_data/stroke_mortalitybyhbr_up_to_2022.csv")) %>% 
  clean_names()

activity_hb_2022 <- read_csv(here("raw_data/stroke_activitybyhbr_up_to_2022.csv")) %>% 
  clean_names()


```

```{r}
activity_hb_2022 %>% 
  filter(hbr == "S92000003" &
           age_group == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```

```{r}
activity_hb_2022 %>% 
  select(where(is.character)) %>% 
  map(unique)
```

Original activity file goes up to 2018/2019. We now have data for 2019/2020, 2020/2021 and 2021/2022 - three extra years. Lets filter and find out how many rows this is. 

```{r}
activity_2019_to_2022 <- activity_hb_2022 %>% 
  filter(financial_year %in% c("2019/20", "2020/21", "2021/22"))
```

Each year contains 4320 records. There are 10 years worth of data currently available so that equates to the 43200 observations we have in our datasets. 

Each year is broken down into:
15 health boards (14 and all Scotland)
3 sexes (M, F, All)
6 age groups (0-44, 45-64, 65-74 years, 75plus, under 75, all)
4 diagnoses (cerebrovascular disease, stroke, subarachnoid haemorrhage, TIAs and related syndromes)
4 admission types (Elective, emergency, transfer, all)
15 * 3 * 6 * 4 * 4 = 4320

Now that I have an understanding of the data I feel I can confidently merge the datasets so we have data from 2009/10 up to 2021/22.

```{r}
activity <- bind_rows(activity_hb, activity_2019_to_2022)
```

This gives the expected number of rows (43200 + (3 * 4320)).

```{r}
activity %>% 
  filter(hbr == "S92000003" &
           age_group == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```


```{r}
other_cvd <- activity %>% 
  filter(!diagnosis == "Cerebrovascular Disease") %>% 
  group_by(financial_year, hbr, admission_type, age_group, sex) %>% 
  summarise(number_of_discharges_other_cvd = sum(number_of_discharges),
            crude_rate_other_cvd = sum(crude_rate),
            easr_other_cvd = sum(easr)) %>% 
  mutate(diagnosis = "Other CVD", .after = sex) 
  

cvd_only <- activity %>% 
  filter(diagnosis == "Cerebrovascular Disease")
```

```{r}
all <- left_join(other_cvd, cvd_only, by = 
            c("financial_year", "hbr", "admission_type", "age_group", "sex"))

all <- all %>% 
  mutate(number_of_discharges = number_of_discharges - number_of_discharges_other_cvd,
         crude_rate = crude_rate - crude_rate_other_cvd, 
         easr = easr - easr_other_cvd) %>% 
  select(-ends_with("cvd"), -diagnosis.y) %>% 
  rename(diagnosis = diagnosis.x)
```




```{r}
activity <- activity %>% 
  select(!ends_with("qf"))
```


```{r}
new_activity <- bind_rows(activity, all)
```

```{r}
new_activity %>% 
  filter(hbr == "S92000003" &
           age_group == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  ggplot(aes(financial_year, number_of_discharges)) +
  geom_col(aes(fill = diagnosis), position = "dodge")
```

```{r}
new_activity %>% 
    filter(hbr == "S92000003" &
           age_group == "All" &
           sex == "All" &
           admission_type == "All") %>% 
  filter(!diagnosis == "Cerebrovascular Disease") %>% 
  group_by(financial_year, hbr, admission_type, age_group, sex) %>% 
  summarise(total = sum(number_of_discharges)) %>% 
    ggplot(aes(financial_year, total)) +
  geom_col()



```

