---
title: "Multiple Linear Regression - Mortality"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---


```{r}
library(tidyverse)
library(here)
library(GGally) # ggpairs
library(modelr) # add_residuals and add_predictions
library(ggfortify) # autoplot
library(broom) # glance - for checking AIC, BIC of models
```


```{r}
activity_hb <- read_csv(here("clean_data/activity_hb.csv")) 
mortality_hb <- read_csv(here("clean_data/mortality_hb.csv")) 
```


```{r}
mortality_hb_for_fitting_easr <- mortality_hb %>% 
  select(-hbr, -crude_rate, -number_of_deaths) %>% 
  # Remove all rows which are combinations of other rows
  filter(hbr_name != "Scotland",
         !age %in% c("All", "under 75"),
         sex != "All",
         diagnosis != "Cerebrovascular Disease") 
```

## Model 1 - Age

```{r, message = FALSE}
ggpairs(mortality_hb_for_fitting_easr, progress = FALSE)
```


```{r}
model_mort_1 <- lm(log(1 + easr) ~ age, 
                      data = mortality_hb_for_fitting_easr)

#autoplot(model_mort_1)

summary(model_mort_1)
```

Wow we have an R2 of 0.5 already. 

## Model 2 - diagnosis

```{r}
mortality_hb_remaining_resid <- mortality_hb_for_fitting_easr %>% 
  add_residuals(model_mort_1) %>% 
  select(-easr, -age)


#ggpairs(mortality_hb_remaining_resid, progress = FALSE)
```



```{r}
model_mort_2 <- lm(log(1 + easr) ~ age + diagnosis, 
                      data = mortality_hb_for_fitting_easr)

#autoplot(model_mort_2)

summary(model_mort_2)
```

R2 upt o 0.64 now. 

## Model 3 - health board

```{r}
mortality_hb_remaining_resid <- mortality_hb_for_fitting_easr %>% 
  add_residuals(model_mort_2) %>% 
  select(-easr, -age, -diagnosis)
```


```{r, message = FALSE}
#ggpairs(mortality_hb_remaining_resid, progress = FALSE)
```

```{r}
model_mort_3 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name, 
                      data = mortality_hb_for_fitting_easr)

#autoplot(model_mort_3)

summary(model_mort_3)
```

Not huge improvement in R2 up to 0.68 now. Lots of the health boareds are not significant. 
Orkney, Shetland, WI and Borders are only ones with 3 stars. Dumfries has 2 and Glasgow has 1. 


## Model 4 - year

No point in adding residuals nad checking ggpairs as year and sex are only variables left. We need year so lets add it first. 

```{r}
model_mort_4 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year, 
                      data = mortality_hb_for_fitting_easr)

#autoplot(model_mort_4)

summary(model_mort_4)
```

```{r}
anova(model_mort_3, model_mort_4)
```

It is significant to add year. 

## Model 5 - sex



```{r}
model_mort_5 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex, 
                      data = mortality_hb_for_fitting_easr)

#autoplot(model_mort_5)

summary(model_mort_5)

anova(model_mort_4, model_mort_5)
```

Not significant to add sex (but might be if we look at interactions) so lets leave it in for now. 


Lets try interactions, as I did for discharges. We added:
admission_type:diagnosis
age:admission_type
age:diagnosis
age:diagnosis:admission_type
sex:diagnosis

**No admission type in this data so lets try:**
diagnosis:age
diagnosis:sex
diagnosis:hbr_name
diagnosis:year

age:sex
age:hbr_name
age:year

hbr_name:sex
hbr_name:year

sex:year


## Model 6 - interactions - diagnosis:age

```{r}
model_mort_6a <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6b <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6c <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6d <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6e <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   age:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6f <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   age:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6g <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   age:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6h <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   hbr_name:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6i <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   hbr_name:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_6j <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   sex:year, 
                      data = mortality_hb_for_fitting_easr)

```

```{r}
mod1_stats <- glance(model_mort_1) %>% 
  mutate(model_name = "1", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod2_stats <- glance(model_mort_2) %>% 
  mutate(model_name = "2", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod3_stats <- glance(model_mort_3) %>% 
  mutate(model_name = "3", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod4_stats <- glance(model_mort_4) %>% 
  mutate(model_name = "4", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod5_stats <- glance(model_mort_5) %>% 
  mutate(model_name = "5", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6a_stats <- glance(model_mort_6a) %>% 
  mutate(model_name = "6a", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6b_stats <- glance(model_mort_6b) %>% 
  mutate(model_name = "6b", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6c_stats <- glance(model_mort_6c) %>% 
  mutate(model_name = "6c", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6d_stats <- glance(model_mort_6d) %>% 
  mutate(model_name = "6d", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6e_stats <- glance(model_mort_6e) %>% 
  mutate(model_name = "6e", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6f_stats <- glance(model_mort_6f) %>% 
  mutate(model_name = "6f", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6g_stats <- glance(model_mort_6g) %>% 
  mutate(model_name = "6g", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6h_stats <- glance(model_mort_6h) %>% 
  mutate(model_name = "6h", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6i_stats <- glance(model_mort_6i) %>% 
  mutate(model_name = "6i", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6j_stats <- glance(model_mort_6j) %>% 
  mutate(model_name = "6j", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6a_stats, mod6b_stats, mod6c_stats, mod6d_stats, mod6e_stats,
  mod6f_stats, mod6g_stats, mod6h_stats, mod6i_stats, mod6j_stats)
```

```{r}
model_stat_comparison %>% 
  ggplot(aes(model_name, AIC)) + 
  geom_point()
```

diagnosis:age has a huge impact lets add this
6b and 6f look like they may also have an impact
6b is diagnosis:sex
6f is age:hbr_name


```{r}
model_mort_6 <-  model_mort_6a

mod6_stats <- glance(model_mort_6) %>% 
  mutate(model_name = "6", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)
```

```{r}
anova(model_mort_5, model_mort_6)
```

It is significant to add age:diagnosis

## Model 7 - interactions - diagnosis:sex


```{r}
model_mort_7b <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age + diagnosis:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7c <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age + diagnosis:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7d <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age + diagnosis:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7e <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age + age:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7f <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age + age:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7g <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                  diagnosis:age +  age:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7h <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age + hbr_name:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7i <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age + hbr_name:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_7j <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age + sex:year, 
                      data = mortality_hb_for_fitting_easr)
```

```{r}


mod7b_stats <- glance(model_mort_7b) %>% 
  mutate(model_name = "7b", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7c_stats <- glance(model_mort_7c) %>% 
  mutate(model_name = "7c", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7d_stats <- glance(model_mort_7d) %>% 
  mutate(model_name = "7d", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7e_stats <- glance(model_mort_7e) %>% 
  mutate(model_name = "7e", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7f_stats <- glance(model_mort_7f) %>% 
  mutate(model_name = "7f", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7g_stats <- glance(model_mort_7g) %>% 
  mutate(model_name = "7g", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7h_stats <- glance(model_mort_7h) %>% 
  mutate(model_name = "7h", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7i_stats <- glance(model_mort_7i) %>% 
  mutate(model_name = "7i", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7j_stats <- glance(model_mort_7j) %>% 
  mutate(model_name = "7j", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6_stats, mod7b_stats, mod7c_stats, mod7d_stats, mod7e_stats,
  mod7f_stats, mod7g_stats, mod7h_stats, mod7i_stats, mod7j_stats)
```


```{r}
model_stat_comparison %>% 
  ggplot(aes(model_name, BIC)) + 
  geom_point() +
  scale_y_continuous(limits = c(10000, 13000))
```

f is lowest AIC but b is lowest BIC

lets add b - diagnosis:sex

```{r}
model_mort_7 <-  model_mort_7b

mod7_stats <- glance(model_mort_7) %>% 
  mutate(model_name = "7", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)
```

```{r}
anova(model_mort_6, model_mort_7)
```

Significant to add diagnosis:sex (this means sex has to stay in model)

## Model 8 - interactions - age:sex

```{r}
model_mort_8c <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age + diagnosis:sex + diagnosis:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8d <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age  + diagnosis:sex+ diagnosis:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8e <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8f <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8g <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                  diagnosis:age  + diagnosis:sex+  age:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8h <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ hbr_name:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8i <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ hbr_name:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_8j <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ sex:year, 
                      data = mortality_hb_for_fitting_easr)
```


```{r}
mod8c_stats <- glance(model_mort_8c) %>% 
  mutate(model_name = "8c", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8d_stats <- glance(model_mort_8d) %>% 
  mutate(model_name = "8d", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8e_stats <- glance(model_mort_8e) %>% 
  mutate(model_name = "8e", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8f_stats <- glance(model_mort_8f) %>% 
  mutate(model_name = "8f", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8g_stats <- glance(model_mort_8g) %>% 
  mutate(model_name = "8g", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8h_stats <- glance(model_mort_8h) %>% 
  mutate(model_name = "8h", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8i_stats <- glance(model_mort_8i) %>% 
  mutate(model_name = "8i", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod8j_stats <- glance(model_mort_8j) %>% 
  mutate(model_name = "8j", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6_stats, mod7_stats, mod8c_stats, mod8d_stats, mod8e_stats,
  mod8f_stats, mod8g_stats, mod8h_stats, mod8i_stats, mod8j_stats)
```


```{r}
model_stat_comparison %>% 
  ggplot(aes(model_name, BIC)) + 
  geom_point() +
  scale_y_continuous(limits = c(11000, 12000))
```

AIC
8f is really giving much lower AIC than others age:hbr_name
8e is has a very slightly lower AIC than model 7 age:sex

BIC
model 7     11593.65
model 8e    11583.96
model 8f    11597.05


```{r}
model_mort_8 <-  model_mort_8e

mod_8_stats <- glance(model_mort_8) %>% 
  mutate(model_name = "8", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)
```

```{r}
anova(model_mort_7, model_mort_8)
```

It is signficanat to add age:sex to model

## Model 9 - interactions - age:hbr_name

```{r}
model_mort_9c <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age + diagnosis:sex + age:sex + diagnosis:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_9d <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age  + diagnosis:sex+ age:sex + diagnosis:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_9f <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_9g <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                  diagnosis:age  + diagnosis:sex+  age:sex + age:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_9h <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + hbr_name:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_9i <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + hbr_name:year, 
                      data = mortality_hb_for_fitting_easr)

model_mort_9j <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + sex:year, 
                      data = mortality_hb_for_fitting_easr)
```

```{r}
mod9c_stats <- glance(model_mort_9c) %>% 
  mutate(model_name = "9c", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod9d_stats <- glance(model_mort_9d) %>% 
  mutate(model_name = "9d", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod9f_stats <- glance(model_mort_9f) %>% 
  mutate(model_name = "9f", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod9g_stats <- glance(model_mort_9g) %>% 
  mutate(model_name = "9g", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod9h_stats <- glance(model_mort_9h) %>% 
  mutate(model_name = "9h", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod9i_stats <- glance(model_mort_9i) %>% 
  mutate(model_name = "9i", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod9j_stats <- glance(model_mort_9j) %>% 
  mutate(model_name = "9j", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6_stats, mod7_stats, mod_8_stats, mod9c_stats, mod9d_stats,
  mod9f_stats, mod9g_stats, mod9h_stats, mod9i_stats, mod9j_stats)
```

```{r}
model_stat_comparison %>% 
  ggplot(aes(model_name, AIC)) + 
  geom_point() +
  scale_y_continuous(limits = c(11000, 12000))
```

Hmmm possible shouldn't add 8f age:hbr_name but AIC improves a lot and BIC only increases by 1 unit. 
age:hbr_name does also make sense

```{r}
model_mort_9 <-  model_mort_8f

mod_9_stats <- glance(model_mort_9) %>% 
  mutate(model_name = "9", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)
```

```{r}
anova(model_mort_8, model_mort_9)
```

It is significant to add age:hbr_name

## Model 10 - 3-way int - diagnosis:age:sex

Lets stop there with 2-way interactions and try some 3 way

diagnosis:age:sex is the obvious one to try but lets try the others too
diagnosis:age:hbr_name
diagnosis:sex:hbr_name
age:sex:hbr_name

```{r}
model_mort_10A <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name +
                     diagnosis:age:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_10B <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name +
                     diagnosis:age:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_10C <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name +
                     diagnosis:sex:hbr_name, 
                      data = mortality_hb_for_fitting_easr)

model_mort_10D <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name +
                     hbr_name:age:sex, 
                      data = mortality_hb_for_fitting_easr)

```

```{r}
mod10A_stats <- glance(model_mort_10A) %>% 
  mutate(model_name = "10A", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod10B_stats <- glance(model_mort_10B) %>% 
  mutate(model_name = "10B", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod10C_stats <- glance(model_mort_10C) %>% 
  mutate(model_name = "10C", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod10D_stats <- glance(model_mort_10D) %>% 
  mutate(model_name = "10D", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)


model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6_stats, mod7_stats, mod_8_stats, mod_9_stats, mod10A_stats,
  mod10B_stats, mod10C_stats, mod10D_stats)
```

```{r}
model_stat_comparison %>% 
  ggplot(aes(model_name, BIC)) + 
  geom_point() +
  scale_y_continuous(limits = c(10000, 13000))
```

10A and 10B have lower AIC than model 9
10A has slightly lower BIC than model 9. 10B has much higher BIC
Lets add 10A diagnosis:age:sex and call it quits


```{r}
model_mort_10 <-  model_mort_10A

mod_10_stats <- glance(model_mort_10) %>% 
  mutate(model_name = "10", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)
```

```{r}
anova(model_mort_9, model_mort_10)
```

It is significant to add age:sex:diagnosis

## MODEL 10 FINAL MODEL

log(1 + easr) ~ age + diagnosis + hbr_name + year + sex + diagnosis:age + 
    diagnosis:sex + age:sex + age:hbr_name + diagnosis:age:sex
    
    
    
```{r}
model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6_stats, mod7_stats, mod_8_stats, mod_9_stats, mod_10_stats) %>% 
  mutate(model_name = as.numeric(model_name))
```
    
```{r}
model_stat_comparison %>% 
  ggplot(aes(model_name, BIC)) + 
  geom_point() #+
  #scale_y_continuous(limits = c(10000, 13000))
```

