---
title: "PHS Stroke Data Analysis Project"
output:
  html_document:
    toc: yes
    toc_float: true
    toc_depth: '2'
    highlight: tango
    df_print: paged
---

## Assumptions made during cleaning

For activity data the diagnosis column "Cerebrovascular disease" covers everything and is essentially the "All" category. There were originally 3 sub-categories but these didn't add up to the total value under "Cerebrovascular disease". This is because there are some other diagnosis (with ICD codes I62, I65, I66-69) which fall outwith these sub-categories. For this reason a 4th sub-category was created called "Other CVD". 

For the mortality data, "TIAs and related syndromes" are included in the "Cerebrovascular disease" category and not separated out. 

There were a lot of missing values for Orkney, Shetland and Western Isles due to confidentiality. These were converted to zeros. EXPLAIN WHY

## Assumptions made during analysis

To determine which diagnosis is most common the number of diagnosis and number of deaths values were used, rather than the crude rates or easr. It was felt it was more important to know the actual number than a number adjusted for 100,000 of population (crude rate) or age adjusted (easr).

Sometimes the islands were combined.

```{r}
library(tidyverse)
library(here)
library(sf)
library(leaflet)
library(htmlwidgets)
library(modelr) # add_residuals and add_predictions
library(broom) # glance - for checking AIC, BIC of models
```

```{r}
source(here("theme_palette_etc/plot_theme.R"))
#source(here("theme_palette_etc/palette.R"))
```

```{r}
activity_hb <- read_csv(here("clean_data/activity_hb.csv"))

mortality_hb <- read_csv(here("clean_data/mortality_hb.csv"))
```

## Q1 Most common stroke diagnosis?

There are two datasets which need analysed to answer this questions - the activity dataset which details the number of discharges and the mortality which details the number of deaths. It should be noted that one patient could have more than one discharge.

The unadultered values are used for this analysis as we are looking for the most common stroke diagnosis.

```{r}
activity_hb %>% 
  # filter so we only have most recent 10 years
  filter(!financial_year %in% c("2009/10", "2010/11", "2011/12")) %>% 
  # filter so we have all Scotland, ages, sex and admission types but not the CVD 
  # total in diagnosis variable.
  filter(hbr == "S92000003" &
           age == "All" &
           sex == "All" &
           admission_type == "All" &
           diagnosis != "Cerebrovascular Disease") %>% 
  # group by diagnosis and then take the mean over the 10 year period
  group_by(diagnosis) %>% 
  summarise(mean_num_discharges = mean(number_of_discharges)) %>% 
  mutate(diagnosis = fct_reorder(diagnosis, mean_num_discharges)) %>% 
  ggplot(aes(diagnosis, mean_num_discharges)) +
  geom_col(fill = c("#6d95bf", "#999999", "#9e8fcb", "#f084b6")) +
  theme_cc_project() +
  theme(axis.title.y = element_blank()) +
  labs(title = "Discharges",
       subtitle = "10 year average", 
       y = "Annual Number of Discharges") +
  coord_flip() +
  # code to wrap text so it goes over two lines
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) 

```

Stroke is by far the most common diagnosis for patients who are discharged. 



```{r}
mortality_hb %>% 
  filter(year >= 2012) %>% 
  filter(hbr == "S92000003" &
          age == "All" &
          sex == "All" &
          diagnosis != "Cerebrovascular Disease") %>% 
  group_by(diagnosis) %>% 
  summarise(mean_num_deaths = mean(number_of_deaths)) %>% 
  mutate(diagnosis = fct_reorder(diagnosis, mean_num_deaths)) %>% 
  ggplot(aes(diagnosis, mean_num_deaths)) +
  geom_col(fill = c("#6d95bf", "#999999", "#9e8fcb")) +
  theme_cc_project() +
    theme(axis.title.y = element_blank()) +
  labs(title = "Mortality",
       subtitle = "10 year average", 
       y = "Annual Number of Deaths") +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) 
```


For the patients that die, stroke is also the most common diagnosis but now the "Other CVD" category is much higher than for patients that are discharged. 

It is not easy to compare the death and discharge figures as they cover different time periods. Discharges are financial year and deaths are calendar year. 

Incidence data was sources from excel files related to the PHS Stroke report but these only subcategorised cerebrovascular disease and stroke.

## Q2 Demographics?

### Age

```{r, message = FALSE, warning = FALSE}
activity_hb %>% 
#  mutate(diagnosis = recode(diagnosis,
#          "Subarachnoid Haemorrhage" = "Subarach. Haemorrhage",
#          "TIAs and related syndromes" = "TIAs & related syndromes")) %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD",
                                                  "TIAs and related syndromes"
                                                  ))) %>% 
   filter(!financial_year %in% c("2009/10", "2010/11", "2011/12")) %>% 
  filter(hbr == "S92000003",
         sex == "All",
         admission_type == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(age, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(age, mean_easr)) +
  geom_col(aes(fill = diagnosis)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#9e8fcb", "#6d95bf", "#f084b6")) +
  theme_cc_project() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 16, colour = "grey50")) +
  labs(title = "Discharges",
#       subtitle = "10 year average",
       y = "Discharge Rate (EASR)",
       x = "Age")
```

### Sex

```{r, warning = FALSE, message = FALSE}
activity_sex_diagnosis <- activity_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", "Subarachnoid Haemorrhage",
       "Other CVD",  "TIAs and related syndromes"))) %>% 
     filter(!financial_year %in% c("2009/10", "2010/11", "2011/12")) %>% 
  filter(hbr == "S92000003",
         sex != "All",
         admission_type == "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
  group_by(sex, diagnosis) %>% 
  summarise(mean_discharges = mean(number_of_discharges),
            mean_crude_rate = mean(crude_rate),
            mean_easr = mean(easr))
  
  
  ggplot(activity_sex_diagnosis, aes(sex, mean_discharges)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_cc_project() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey50"),
        axis.title.x = element_blank()) +
    labs(title = "Number of Discharges by Sex & CVD Type",
       y = "Number of Discharges")


  ggplot(activity_sex_diagnosis, aes(sex, mean_easr)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y") +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_cc_project() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey50"),
                axis.title.x = element_blank()) +
    labs(title = "Discharges",
        y = "Discharge Rate (EASR)")
    

```




## Q4 Mortality

### Mortality by year

```{r}
mortality_hb %>% 
  filter(hbr == "S92000003",
         sex == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, easr)) +
  geom_point() +
  theme_fc() #+
 # scale_y_continuous(limits = c(2000, 5000))
```





### Age

```{r}
mortality_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
                                                  "Subarachnoid Haemorrhage",
                                                  "Other CVD"))) %>% 
  filter(year > 2012,
    hbr == "S92000003",
         sex == "All",
         !age %in% c("All", "under 75"), 
         diagnosis != "Cerebrovascular Disease") %>%
# the group_by and summarise were inserted to get rid of horizontal white lines on columns in plot
    group_by(age, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(age, mean_easr)) +
  geom_col(aes(fill = diagnosis)) +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2) +
  scale_fill_manual(values = c("#999999", "#9e8fcb", "#6d95bf")) +
  theme_cc_project() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 16, colour = "grey50")) +
    labs(title = "Mortality",
#       subtitle = "10 year average",
        x = "Age", 
        y = "Mortality Rate (EASR)")


```

### Sex

```{r, warning = FALSE, message = FALSE}
mortality_sex_diagnosis <- mortality_hb %>% 
  mutate(diagnosis = factor(diagnosis, levels = c("Stroke", 
        "Subarachnoid Haemorrhage", "Other CVD"))) %>% 
  filter(year >2012) %>% 
  filter(hbr == "S92000003",
         sex != "All",
         age == "All", 
         diagnosis != "Cerebrovascular Disease") %>%
  group_by(sex, diagnosis) %>% 
  summarise(mean_deaths = mean(number_of_deaths),
            mean_crude_rate = mean(crude_rate),
            mean_easr = mean(easr))
  
  
  ggplot(mortality_sex_diagnosis, aes(sex, mean_deaths)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2) +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_cc_project() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey50"),
        axis.title.x = element_blank()) +
    labs(title = "Mortality by Sex and CVD Type",
       y = "Number of Deaths")


  ggplot(mortality_sex_diagnosis, aes(sex, mean_easr)) +
  geom_col(aes(fill = sex)) +
  facet_wrap(~diagnosis, scales = "free_y", nrow = 2) +
  scale_fill_manual(values = c("#999999", "#6d95bf")) +
  theme_cc_project() + 
  theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 14, colour = "grey50"),
        axis.title.x = element_blank()) +
    labs(title = "Mortality",
       y = "Discharge Rate (EASR)")

```



## Q3 Health Board or Council

### Population by health board

```{r}
hb_population <- read_csv(here("raw_data/health_board_populations.csv"))
```

```{r}
hb_population %>% 
  mutate(hb_name = str_remove(hb_name, "NHS ")) %>% 
    mutate(hb_name = fct_reorder(hb_name, population)) %>% 
  mutate(hb_name = recode(hb_name, 
                          "Greater Glasgow and Clyde" = "Grtr Glasgow & Clyde",
                          "Dumfries and Galloway" = "Dumfries & Galloway")) %>% 
  mutate(population = population / 1000000) %>% 
ggplot(aes(hb_name, population)) +
  geom_col(fill = "#999999") +
  coord_flip() +
  labs(title = "Health Board Populations",
       y = "Population (Millions)") +
  theme_cc_project() +
  theme(axis.title.y = element_blank()) +
  scale_y_continuous(limits = c(0, 1.3))
  
  #scale_y_discrete(expand = c(0,0))

```

### Age distribution

```{r}
hb_age_pop_over_under_75 <- read_csv(here("clean_data/hb_population_2021_by_age.csv"))
```

```{r}
hb_age_pop_over_under_75 %>% 
    select(area_code, area_name, sex, all_ages, under_75, over_75) %>% 
  mutate(percent_over_75 = over_75 / all_ages * 100) %>% 
  mutate(area_name = fct_reorder(area_name, percent_over_75)) %>% 
  mutate(area_name = recode(area_name, 
                          "Greater Glasgow and Clyde" = "Grtr Glasgow & Clyde",
                          "Dumfries and Galloway" = "Dumfries & Galloway")) %>% 
  filter(area_name != "Scotland") %>% 
  filter(sex == "Persons") %>% 
  ggplot()+
  geom_col(aes(area_name, percent_over_75), fill = "#6d95bf") +
  coord_flip() +
  labs(title = "Percentage Over 75",
       y = "Percentage Over 75 (%)") +
  theme_cc_project() +
  theme(axis.title.y = element_blank())

```


### Discharges by Health Board


```{r}
activity_hb %>% 
    mutate(start_fin_year = as.numeric(str_extract(financial_year, "^[0-9]{4}")), 
         .after = financial_year) %>% 
  select(-financial_year, -hbr) %>%
    filter(hbr_name == "Scotland",
         sex == "All",
         admission_type == "All", 
         age == "All",
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(start_fin_year, easr)) +
  geom_point(colour = "#6d95bf", size = 3) +
  scale_y_continuous(limits = c(500, 700)) +
  theme_cc_project() +
  labs(title = "Scotland Discharge Rates",
       x = "Year", 
       y = "Discharge Rate (EASR) \n")
```

```{r}
islands <- activity_hb %>% 
  filter(hbr_name %in% c("Orkney", "Shetland", "Western Isles")) %>% 
  group_by(financial_year, admission_type, age, sex, diagnosis) %>% 
  summarise(number_of_discharges = sum(number_of_discharges),
            crude_rate = mean(crude_rate),
            easr = mean(easr)) %>% 
  mutate(hbr_name = "Islands")

activity_hb_islands <- activity_hb %>% 
  filter(!hbr_name %in% c("Orkney", "Shetland", "Western Isles")) %>% 
  bind_rows(islands)
```


```{r}
activity_hb_islands %>% 
    mutate(start_fin_year = as.numeric(str_extract(financial_year, "^[0-9]{4}")), 
         .after = financial_year) %>% 
  select(-financial_year, -hbr) %>%
  filter(hbr_name != "Scotland",
         sex == "All",
         admission_type == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(start_fin_year, easr)) +
  geom_point(aes(colour = hbr_name)) +
  geom_smooth(method = lm, colour = "black", linewidth = 0.4, se = FALSE) +
  facet_wrap(~hbr_name) +  
#  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., 
#                                        sep = "~~~~"))) +
# plots were coloured according to whether they changed by over or under 100 over the 13 year period
      scale_colour_manual(values = c("#6d95bf", "grey30", "#f084b6", "grey30","#6d95bf", "#f084b6", "#6d95bf", "grey30","grey30", "#6d95bf", "#f084b6", "grey30")) +
    theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 10, colour = "grey30"),
        axis.text.y = element_text(size = 8),
        panel.background = element_blank(),
        panel.grid.minor = element_line(colour = "grey50", linetype = "dotted"),
        ) +
  labs(x = "Year",
        y = "Discharge Rate (EASR)") +
  scale_y_continuous(minor_breaks = seq(200, 900, 100))
```




### Mortality by Health Board

```{r}
mortality_hb %>% 
  select(-hbr) %>%
    filter(hbr_name == "Scotland",
         sex == "All",
         age == "All",
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, easr)) +
  geom_point(colour = "#6d95bf", size = 3) +
  scale_y_continuous(limits = c(0, 125)) +
  theme_cc_project() +
  labs(title = "Scotland Mortality Rates",
       x = "Year", 
       y = "Mortality Rate (EASR) \n")
```






```{r}
islands_mortality <- mortality_hb %>% 
  filter(hbr_name %in% c("Orkney", "Shetland", "Western Isles")) %>% 
  group_by(year, age, sex, diagnosis) %>% 
  summarise(number_of_deaths = sum(number_of_deaths),
            crude_rate = mean(crude_rate),
            easr = mean(easr)) %>% 
  mutate(hbr_name = "Islands")

mortality_hb_islands <- mortality_hb %>% 
  filter(!hbr_name %in% c("Orkney", "Shetland", "Western Isles")) %>% 
  bind_rows(islands_mortality)

mortality_hb_islands %>% 
  filter(hbr_name != "Scotland",
         sex == "All",
         age == "All", 
         diagnosis == "Cerebrovascular Disease") %>% 
  ggplot(aes(year, easr)) +
  geom_point(colour = "#f084b6") +
  geom_smooth(method = lm, colour = "black", linewidth = 0.4, se = FALSE) +
  facet_wrap(~hbr_name) +  
#  stat_regline_equation(aes(label = paste(..eq.label.., ..rr.label.., 
#                                        sep = "~~~~"))) +
    theme(legend.position = "none",
        # changes font size of faceted plot titles. 
        strip.text = element_text(size = 10, colour = "grey30"),
        axis.text.y = element_text(size = 8),
        panel.background = element_blank(),
        panel.grid.minor = element_line(colour = "grey50", linetype = "dotted"),
        ) +
  labs(x = "Year",
        y = "Mortality Rate (EASR)") #+
  #scale_y_continuous(minor_breaks = seq(0, 900, 25))
```










## Q5 Future Predictions

```{r}
mortality_hb_for_fitting_easr <- mortality_hb %>% 
  select(-hbr, -crude_rate, -number_of_deaths) %>% 
  # Remove all rows which are combinations of other rows
  filter(hbr_name != "Scotland",
         !age %in% c("All", "under 75"),
         sex != "All",
         diagnosis != "Cerebrovascular Disease") 
```

### R2, AIC and BIC

Load all models so we can draw AIC and BIC graphs
```{r}
model_mort_1 <- lm(log(1 + easr) ~ age, 
                      data = mortality_hb_for_fitting_easr)
model_mort_2 <- lm(log(1 + easr) ~ age + diagnosis, 
                      data = mortality_hb_for_fitting_easr)
model_mort_3 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name, 
                      data = mortality_hb_for_fitting_easr)
model_mort_4 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year, 
                      data = mortality_hb_for_fitting_easr)
model_mort_5 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex, 
                      data = mortality_hb_for_fitting_easr)
model_mort_6 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age, 
                      data = mortality_hb_for_fitting_easr)
model_mort_7 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                    diagnosis:age + diagnosis:sex, 
                      data = mortality_hb_for_fitting_easr)
model_mort_8 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex, 
                      data = mortality_hb_for_fitting_easr)
model_mort_9 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name, 
                      data = mortality_hb_for_fitting_easr)
model_mort_10 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name +
                     diagnosis:age:sex, 
                      data = mortality_hb_for_fitting_easr)

model_mort_11 <- lm(log(1 + easr) ~ age + diagnosis + hbr_name + year + sex +
                   diagnosis:age  + diagnosis:sex+ age:sex + age:hbr_name +
                     diagnosis:age:sex + year:age + year:sex + year:hbr_name + 
                     year:diagnosis, 
                      data = mortality_hb_for_fitting_easr)
```

Pull out all the stats into one dataframe - really need to functionalise this.

```{r}
mod1_stats <- glance(model_mort_1) %>% 
  mutate(model_name = "1", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod2_stats <- glance(model_mort_2) %>% 
  mutate(model_name = "2", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod3_stats <- glance(model_mort_3) %>% 
  mutate(model_name = "3", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod4_stats <- glance(model_mort_4) %>% 
  mutate(model_name = "4", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod5_stats <- glance(model_mort_5) %>% 
  mutate(model_name = "5", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod6_stats <- glance(model_mort_6) %>% 
  mutate(model_name = "6", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod7_stats <- glance(model_mort_7) %>% 
  mutate(model_name = "7", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod_8_stats <- glance(model_mort_8) %>% 
  mutate(model_name = "8", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod_9_stats <- glance(model_mort_9) %>% 
  mutate(model_name = "9", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod_10_stats <- glance(model_mort_10) %>% 
  mutate(model_name = "10", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mod_11_stats <- glance(model_mort_11) %>% 
  mutate(model_name = "11", .before = r.squared) %>% 
  select(model_name, r.squared, adj.r.squared, AIC, BIC)

mortality_model <- model_mort_11 

model_stat_comparison <- bind_rows(
  mod1_stats, mod2_stats, mod3_stats, mod4_stats, mod5_stats, 
  mod6_stats, mod7_stats, mod_8_stats, mod_9_stats, mod_10_stats, mod_11_stats) %>% 
  mutate(model_name = as.numeric(model_name))
```


```{r}
model_stat_comparison %>% 
  ggplot() + 
  geom_point(aes(model_name, r.squared), colour = "#6d95bf", size = 4) +
#  geom_point(aes(model_name, adj.r.squared), colour = "#f084b6", size = 3, shape = 17) +
  theme_cc_project()


colours <- c("AIC" = "#6d95bf", "BIC" = "#f084b6")

model_stat_comparison %>% 
  ggplot() + 
  geom_point(aes(model_name, AIC, colour = "#6d95bf"), size = 4) +
  geom_point(aes(model_name, BIC, colour = "#f084b6"), size = 3, shape = 17) +
  scale_y_continuous(limits = c(10000, 16500)) +
  theme_cc_project() +
  labs(y = "AIC or BIC", 
       x = "Model Number", 
       color = "Legend") +
  scale_color_identity(labels = c("AIC", "BIC"),
    guide = "legend") +
  scale_x_continuous(breaks = 1:11)
  
```

### Real vs Model Values

```{r}
mortality_predictions_2009_2021 <- mortality_hb_for_fitting_easr %>% 
  add_predictions(mortality_model) 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 1300), 
                     breaks = c(200, 400, 600, 800, 1000, 1200))



mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0), limits = c(0, 100)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 100))

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
    geom_abline(slope = 0.8, colour = "black", linewidth = 1) +
    geom_abline(slope = 1.2, colour = "black", linewidth = 1) +
  theme_cc_project() +
  labs(title = "black lines are +/- 20% of real mortality rate",
    x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") #+ 
 #  scale_y_continuous(expand = c(0,0), limits = c(0, 25)) +
 # scale_x_continuous(expand = c(0,0), limits = c(0, 25))
```

#### By Health Board

```{r}
mortality_predictions_2009_2021 <- mortality_hb_for_fitting_easr %>% 
  add_predictions(mortality_model) 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 0.5) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 1300), 
                     breaks = c(200, 400, 600, 800, 1000, 1200)) +
  facet_wrap(~hbr_name) 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0), limits = c(0, 100)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 100)) +
  facet_wrap(~hbr_name) 
```

#### By Age

```{r}
mortality_predictions_2009_2021 <- mortality_hb_for_fitting_easr %>% 
  add_predictions(mortality_model) 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 0.5) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  facet_wrap(~age, scale = "free") 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0), limits = c(0, 100)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 100)) +
  facet_wrap(~age) 
```

#### By diagnosis

```{r}
mortality_predictions_2009_2021 <- mortality_hb_for_fitting_easr %>% 
  add_predictions(mortality_model) 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 0.5) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  facet_wrap(~diagnosis, scale = "free") 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0), limits = c(0, 100)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 100)) +
  facet_wrap(~diagnosis) 
```

#### By sex

```{r}
mortality_predictions_2009_2021 <- mortality_hb_for_fitting_easr %>% 
  add_predictions(mortality_model) 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 0.5) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0)) +
  scale_x_continuous(expand = c(0,0)) +
  facet_wrap(~sex, scale = "free") 

mortality_predictions_2009_2021 %>% 
ggplot(aes(easr, exp(pred))) +
  geom_point(colour = "#999999", alpha = 0.5) +
  geom_abline(colour = "#f084b6", linewidth = 1) +
#  theme_cc_project() +
  labs(x = "Real Mortality Rate",
       y = "Predicted Mortalilty Rate \n") + 
   scale_y_continuous(expand = c(0,0), limits = c(0, 100)) +
  scale_x_continuous(expand = c(0,0), limits = c(0, 100)) +
  facet_wrap(~sex) 
```



### Future Predictions

```{r}
# Create a new fake future dataset for 2022 to 2034 without easr values
mortality_2022_2034 <- mortality_hb_for_fitting_easr %>% 
  mutate(year = year + 13) %>% 
  select(-easr)

# Add predictions from model to future data set. Also add column to label as predictions
mortality_pred_2022_2034 <- mortality_2022_2034 %>% 
  add_predictions(mortality_model) %>% 
  mutate(pred = exp(pred)) %>% 
  rename("easr" = "pred") %>% 
  mutate(real_or_pred = "pred")

# Combine future predictions 2022-2034 with real results 2009-2021
mortality_all_predictions <- mortality_hb_for_fitting_easr %>% 
  mutate(real_or_pred = "real") %>% 
  bind_rows(mortality_pred_2022_2034)
```

#### All mortaltiy data 

```{r}
mortality_all_predictions %>% 
  group_by(year, real_or_pred) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred), size = 3) +
  theme_cc_project() +
  labs(title = "Predicting Mortality Rates 2022 - 2034",
       y = "Mortality Rates (EASR) \n",
       x = "Year"
       ) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real"))
```

#### By health board

```{r}
mortality_all_predictions %>% 
  group_by(year, real_or_pred, hbr_name) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred)) +
  facet_wrap(~hbr_name) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real")) +
  labs(y = "Mortality Rates (EASR) \n",
       x = "Year")
```




#### By Age

```{r}
mortality_all_predictions %>% 
  group_by(year, real_or_pred, age) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred)) +
  facet_wrap(~age, scale = "free_y")
```

#### By diagnosis

```{r}
mortality_all_predictions %>% 
  group_by(year, real_or_pred, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred)) +
  facet_wrap(~diagnosis, scale = "free_y", nrow = 2)
```

#### By sex

```{r}
mortality_all_predictions %>% 
  group_by(year, real_or_pred, sex) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred)) +
  facet_wrap(~sex, scale = "free_y", nrow = 1)
```

#### "Good Predictions"

```{r, message = FALSE}
mortality_all_predictions %>% 
  filter(hbr_name == "Tayside") %>% 
  group_by(year, real_or_pred, hbr_name) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred), size = 3) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real")) +
  theme_cc_project() +
    theme(legend.position = "none") +
  labs(title = "Tayside",
       y = "Mortality Rates (EASR) \n",
       x = "Year") +
  scale_y_continuous(limits = c(30, 100)) +
    scale_x_continuous(limits = c(2008, 2035), n.breaks = 7) 
  
mortality_all_predictions %>% 
  filter(age == "over 75") %>% 
  group_by(year, real_or_pred, age) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred), size = 3) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real")) +
  theme_cc_project() +
    theme(legend.position = "none") +
  labs(title = "Over 75",
       y = "Mortality Rates (EASR) \n",
       x = "Year")

mortality_all_predictions %>% 
  filter(diagnosis == "Stroke") %>% 
  group_by(year, real_or_pred, diagnosis) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred), size = 3) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real")) +
  theme_cc_project() +
    theme(legend.position = "none") +
  labs(title = "Stroke",
       y = "Mortality Rates (EASR) \n",
       x = "Year") +
      scale_x_continuous(limits = c(2008, 2035), n.breaks = 7) 
```

#### "Bad Predictions

```{r, message = FALSE}
mortality_all_predictions %>% 
  filter(hbr_name == "Grampian") %>% 
  group_by(year, real_or_pred, hbr_name) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred), size = 3) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real")) +
  theme_cc_project() +
    theme(legend.position = "none") +
  labs(title = "Grampian",
       y = "Mortality Rates (EASR) \n",
       x = "Year") +
    scale_y_continuous(limits = c(30, 100)) +
    scale_x_continuous(limits = c(2008, 2035), n.breaks = 7) 
  
mortality_all_predictions %>% 
  filter(age == "65-74") %>% 
  group_by(year, real_or_pred, age) %>% 
  summarise(mean_easr = mean(easr)) %>% 
  ggplot(aes(year, mean_easr)) +
  geom_point(aes(colour = real_or_pred), size = 3) +
  scale_color_manual(values = c("#f084b6", "#999999"), 
                     labels = c("Predicted", "Real")) +
  theme_cc_project() +
    theme(legend.position = "none") +
  labs(title = "Age 65 - 74",
       y = "Mortality Rates (EASR) \n",
       x = "Year") +
      scale_x_continuous(limits = c(2008, 2035), n.breaks = 7) 

```



#### RMSE

Website saying that you need to divide rmse by the mean of the predicted value (not sure if its the original data or predicted?)

```{r}
library(Metrics)
```

```{r}
mortality_predictions_2009_2021

rmse(mortality_predictions_2009_2021$easr, exp(mortality_predictions_2009_2021$pred))

```

#### Splitting data into high and low easr

Lets split data into 
1) 2 to infinity
2) 2 - 100
3) > 100


2 to infinity
```{r}
mortality_hb_for_fitting_easr_2_inf <- mortality_hb_for_fitting_easr %>% 
# 1797 rows removed (41% data) where easr = 0 or 1
  filter(easr > 2)  

mortality_predictions_2_inf <- mortality_hb_for_fitting_easr_2_inf %>% 
  add_predictions(mortality_model) 

rmse(mortality_predictions_2_inf$easr, exp(mortality_predictions_2_inf$pred))

```

RMSE is higher without zeros and ones

2 - 100

```{r}
mortality_hb_for_fitting_easr_2_100 <- mortality_hb_for_fitting_easr %>% 
# 1797 rows removed (41% data) where easr = 0 or 1
  filter(easr > 2) %>% 
# 745 rows removed (17% of original data) down to 42% of original data
  filter(easr < 101)

mortality_predictions_2_100 <- mortality_hb_for_fitting_easr_2_100 %>% 
  add_predictions(mortality_model) 

rmse(mortality_predictions_2_100$easr, exp(mortality_predictions_2_100$pred))
```

This improves RMSE a lot but 17 seems a lot for values between 2 and 100!

>100

```{r}
mortality_hb_for_fitting_easr_above_100 <- mortality_hb_for_fitting_easr %>% 
# 1797 rows removed (41% data) where easr = 0 or 1
  filter(easr > 100) 


mortality_predictions_above_100 <- mortality_hb_for_fitting_easr_above_100 %>% 
  add_predictions(mortality_model) 

rmse(mortality_predictions_above_100$easr, exp(mortality_predictions_above_100$pred))
```

Well thats a big numbers, spliting the data doesn't seem to help much






## Causes of deaths in Scotland

```{r}
conditions <- c("Heart Disease", "COVID", "Lung Cancer", "CVD", "Dementia")
percentages <- c(11.1, 7.6, 6.2, 6, 5.6) 

data.frame(conditions, percentages) %>% 
  mutate(conditions = fct_reorder(conditions, percentages)) %>% 
  ggplot(aes(conditions, percentages)) + 
  geom_col(aes(fill = conditions)) +
  coord_flip() +
  theme_cc_project() +
  labs(title = "Top 5 Causes of Death",
       subtitle = "Scotland - 2021",
       y = "Percentage of All Deaths",
       x = "") +
  scale_fill_manual(values = c("Heart Disease" = "#6d95bf", 
                               "COVID" = "#6d95bf", 
                               "Lung Cancer" = "#6d95bf", 
                               "CVD" = "#9e8fcb",
                               "Dementia" = "#6d95bf")) +
  theme(legend.position = "none")
  

#  "#999999", "#9e8fcb", "#6d95bf", "#f084b6"
```


